---
title: "Coffee Shops in Boston"
output:
  html_document:
    df_print: paged
---

```{r echo=FALSE, message=FALSE, results='hide', warning=FALSE}
library(getPass)
library(RPostgreSQL)
library(ggplot2)
library(ggmap)
library(tidyverse)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# get the Boston map
boston <- get_map("Boston,MA", zoom=12)
```

```{r echo=FALSE, message=FALSE, results='hide'}
user <- getPass("PostgreSQL user?")
password <- getPass("PostgreSQL password?")
host <- getPass("PostgreSQL host?")

# connect to the database
con <- dbConnect(dbDriver("PostgreSQL"), 
                 dbname = "postgres",
                 host = host, 
                 port = 5432,
                 user = user, 
                 password = password)
```

```{r echo=FALSE, message=FALSE, results='hide'}
# read SQL query from file
query = ("SELECT * FROM yelp_business_clean")

# store query results in a dataframe 
df <- dbGetQuery(con, query)
```

```{r echo=FALSE, message=FALSE, results='hide'}
# inspect data types
str(df)
```


```{r echo=FALSE, message=FALSE, results='hide'}
# inspect the data
head(df,1)
```

This analysis is based on data obtained from Yelp related to coffee shops in Boston. Relevant information regarding out dataset is include below:

* We used the [Yelp Business Search API](https://www.yelp.com/developers/documentation/v3/business) to collect our data. For more information on how we collected our data, see [this notebook](https://github.com/Lahn-Yop/yelper/blob/master/1_collect_data.ipynb)
* Our search terms consists of `categories=coffee` and `location=boston`
* The dataset is stored in a PostgreSQL database
* There are `r nrow(df)` unique coffee shops in our dataset

While our search focused on Boston, there are many cities that make up the greater Boston-area. The locations of the coffee shops that are represented in our dataset are seen in the map below.

```{r echo=FALSE, fig.align="center", message = FALSE, warning = FALSE}
ggmap(boston) +
  geom_point(data=df, aes(x=longitude, y=latitude, color="red", alpha=0.5)) +
  ggtitle("Coffee Shop Locations") +
  theme(plot.title = element_text(lineheight=.8, face="bold", hjust = 0.5),
        legend.position = "none", 
        axis.title.x=element_blank(),
        axis.text.x=element_blank(), 
        axis.ticks.x=element_blank(), 
        axis.title.y=element_blank(), 
        axis.text.y=element_blank(), 
        axis.ticks.y=element_blank()
        )

```

The average Yelp rating of a coffee shop in Boston is `r round(mean(df$rating),1)`

```{r echo=FALSE, fig.align="center", message = FALSE, warning = FALSE}
ggplot(data=df, aes(x=df$rating)) + 
  geom_histogram(aes(y = ..density.., 
                     fill = ..count..),
                 breaks=seq(1, 5, by = 0.5), 
                 binwidth=0.2) + 
  geom_density() +
  labs(x="Rating", y="Count") +
  theme(plot.title = element_text(hjust = 0.5))
```

However, the average coffee shop rating varies greatly from one city to another. 

```{r echo=FALSE, fig.align="center", message = FALSE, warning = FALSE}
ggplot(data=df, mapping = aes(x=city, y=rating)) +
  geom_boxplot(mapping = aes(fill=city)) +
  theme(legend.position = "none", axis.text.x=element_text(angle=90,hjust=1)) +
  ggtitle("Ratings by City") + 
  theme(plot.title = element_text(lineheight=.8, face="bold", hjust = 0.5))
```

```{r echo=FALSE}
################################################################################################
### WHEN I TRIED TO RUN THIS, IT SAID "Evaluation error: object 'category_coffee' not found." ##
################################################################################################

# Process df into useable metrics for analysis and select vars of interest.

#processed_df <- 
#  df %>% 
#  mutate(coffee_flag = if_else(category_coffee | category_coffeeroasteries, T, F),
#         price_num = str_count(price),
#         trust = scales::rescale(log(rating)*review_count, to = c(0, 100))) %>% 
#  select(name, city, zip_code, 
#         matches("transaction"), coffee_flag, price_num, 
#         review_count, rating, trust) %>% 
#  arrange(-review_count, -rating)
```

```{r echo=FALSE}
#head(processed_df)
```

